---
title: "Global Gender Inequality"
output: html_document
date: "2022-12-13"
---
### Read in data
Located within folder:
* HDI data from  https://hdr.undp.org/data-center/documentation-and-downloads
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41

## Load packages
```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
library(countrycode)
```
```{r}
HDI <- read_csv(here::here("HDR21-22_Composite_indices_complete_time_series.csv"),
                locale = locale(encoding = "latin1"),
                na = " ", skip=0)
World <- st_read("World_Countries_(Generalized)/World_Countries__Generalized_.shp")
```


## Column names
Select columns we want and change country name to country code, using the 'countrycode' package

We could also just join it without this on the country name column

Some notes:

* COW codes = correlates of war codes
* ISO = International Organization for Standardization with 2 or 3 letters...

```{r}
HDIcols <- HDI %>% 
  clean_names() %>% 
  select(iso3, country, gii_2019, gii_2010) %>% 
  mutate(difference=gii_2019-gii_2010) %>% 
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
  mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))
```

## Join

Join the csv to world shape file
```{r}
Join_HDI <- World %>% 
  clean_names() %>% 
  left_join(.,
            HDIcols,
            by = c("iso", "iso_code"))
```

